WI FastPlants: Heritability of number of cotelydons

### 2020-11-04 cotyledon-data-analysis.Rmd
added mosaic plot

The p-value less than 0.05 allows us to also reject the null hypothesis of equality of distributions which provides evidence that the number of cotyledons on the offspring group is significantly higher than in the parent group.

@@

library(ggmosaic)
ggplot(data = dat2) +
  geom_mosaic(aes(x = product(cots), fill=generation))
```

>>>>

The p-value less than 0.05 allows us to also reject the null hypothesis of equality of distributions which provides evidence that the number of cotyledons on the offspring group is significantly higher than in the parent group.
=======
The p-value less than 0.05 allows us to also reject the null hypothesis of equality of distributions which provides evidence that the number of cotyledons on the offspring group is significantly higher than in the parent group.

@@

library(ggmosaic)
ggplot(data = dat2) +
  geom_mosaic(aes(x=product(cots), fill=generation))
```
